Combinatorics of the geometry of Wilson loop diagrams

### 2018-12-19 General WLD combinatorics.tex
changes I shouldn't have made while others were working

\title{Put Title here}
%\author{}
%\date{}

\begin{document}

@@

\begin{dfn} \label{VPropdfn}
Let $W = (\cP, [n])$.
\begin{enumerate}
\item For $p \in \cP$, let $V(p) = \{i_p, i_p+1, j_p, j_p+1\}$ be the set of vertices supporting $p$. Then, for $P \subseteq \cP$, the set $V(P) = \cup_{p \in P} V(p)$ is the vertex support of $P$.
\item For $V \subseteq [n]$, write $\Prop(V) = \{ p \in \cP | V(p) \cap V \neq \emptyset \} $.
\item For $P \subseteq \cP$, define $F(P) = V(P^c)^c$ to be the set of vertices in $[n]$ that only support propagators in the set $P$.
\end{enumerate}
\end{dfn}

Note that $F(\emptyset)$ is the set of vertices that are not in the support of any propagators. \sanote{did we settle on a term here? I'd like to make this a definition}

@@

\begin{proof}
Since the vertices of $\tau(W)$ are labeled by the edges of $W$, which are cyclically ordered, this gives an ordering to the vertices. Furthermore, since the outer \hlfix{circle of $W$ is a cycle}{sounds awkward in the new notation}, the outer face of $\tau(W)$ is also a cycle. Since $W$ is admissible, no pairs of propagators cross. Therefore, it is a planar embedding. Similarly, $W$ does not admit any propagators of the form $p = (i, i+1)$; therefore there is exactly one edge connecting any two adjacent edges of $\tau(W)$. Finally, there does not exist two propagators $p,q$ such that both $p$ and $q$ start at edge $i$ and end at edge $j$. Therefore, no other two vertices of $\tau(W)$ can be connected by more than one edge. Finally, the embedding of $\tau(W)$ is induced from the embedding of the graph $W$.
 \end{proof}

@@

Every triangulated piece $t$ of an admissible Wilson loop diagram $W$ corresponds to a subdiagram of $W$ by taking the set of propagators $P$ corresponding to edges of $t$ and then taking the subdiagram $W_P = (P, V(P))$.  Conversely, given a subdiagram $W_P = (P, V(P))$ of $W$ we can obtain a subgraph of $\tau(W)$, called $t$, as follows:
\begin{itemize}
\item The vertex set of the subgraph $t$ is
  \begin{itemize}
  \item \hlfix{the vertices of $\tau(W)$ corresponding to edges of $W$ defined by cyclically consecutive elements of $V(P)$ as a subset of $[n]$}{changed to simplify with existing notation, but now it contradicts below}
  \end{itemize}
\item The edge set of the subgraph is
  \begin{itemize}
  \item the edges of $\tau(W)$ corresponding to propagators of $P$
  \item along with the outer edges of $\tau(W)$ for which both their end points are in the vertex set
  \end{itemize}
\end{itemize}
Note that the subgraph $t$ only depends on $P$, \hlfix{not the vertex set of the subdiagram $W_P$}{really? why?}, but it is not the subgraph of $\tau(W)$ consisting only of edges corresponding to propagators of $P$.

@@

Agarwala and Marcott show ***cite this*** that the dimension of the positroid cell defined by a Wilson loop diagram $(\cP, [n])$ has dimension $3|\cP|$. Their proof is geometric and elegant, but it is not easy to track the effect of a particular propagator.

The dimension of a positroid cell is the same as the number of plusses in the associated Le diagram ***cite something***, and so with Algorithm~\ref{alg:put GN on WLD} along with the algorithm for passing from a Grassmann necklace to a Le diagram (reversing Oh's algorithm) described by some of us in \cite{reversingOh}, we can, at the cost of a bit of messy grunt work, give a different recursive proof of the $3|\cP|$-dimensionality that explicitly describes the changes in the positions of the plusses in the Le diagram.

@@

{\color{red}Maybe proved that inadmissible diagrams, while they correspond to matroids, can't be mapped to the positroids of the correct dimension? }

>>>>

\title{Combinatorics of the geometry of Wilson loop diagrams}
\author{Susama Agarwala, Si\^an Fryer, and Karen Yeats}
%\date{}

\begin{document}
\maketitle

@@

\begin{dfn} \label{VPropdfn}
Let $W = (\cP, [n])$.
\begin{enumerate}
\item For $p \in \cP$, let $V(p) = \{i_p, i_p+1, j_p, j_p+1\}$ be the set of vertices supporting $p$. Then, for $P \subseteq \cP$, the set $V(P) = \cup_{p \in P} V(p)$ is the vertex support of $P$.
\item For $V \subseteq [n]$, write $\Prop(V) = \{ p \in \cP | V(p) \cap V \neq \emptyset \} $.
\item For $P \subseteq \cP$, define $F(P) = V(P^c)^c$ to be the set of vertices in $[n]$ that do not support any propagators outside the set $P$.
\end{enumerate}
\end{dfn}

Note that $F(\emptyset)$ is the set of vertices that are not in the support of any propagators. \note{mention that $F(\emptyset)$ is also called nonsupporting and also phrase as a note that old lemma about $F(P) = stuff - stuff$.}

@@

\begin{proof}
Since the vertices of $\tau(W)$ are labeled by the edges of $W$, which are cyclically ordered, this gives an ordering to the vertices and the outer face of $\tau(W)$ is a cycle. Since $W$ is admissible, no pairs of propagators cross. Therefore, it is a planar embedding. Similarly, $W$ does not admit any propagators of the form $p = (i, i+1)$; therefore there is exactly one edge connecting any two adjacent edges of $\tau(W)$. Finally, there does not exist two propagators $p,q$ such that both $p$ and $q$ start at edge $i$ and end at edge $j$. Therefore, no other two vertices of $\tau(W)$ can be connected by more than one edge. Finally, the embedding of $\tau(W)$ is induced from the embedding of the graph $W$.
 \end{proof}

@@

Every triangulated piece $t$ of an admissible Wilson loop diagram $W$ corresponds to a subdiagram of $W$ by taking the set of propagators $P$ corresponding to edges of $t$ and then taking the subdiagram $W_P = (P, V(P))$.  Conversely, given a subdiagram $W_P = (P, V(P))$ of $W$ we can obtain a subgraph of $\tau(W)$, called $t$, as follows:
\begin{itemize}
\item The vertex set of the subgraph $t$ is
  \begin{itemize}
  \item the vertices of $\tau(W)$ corresponding to edges of $W$ defined by cyclically consecutive elements of $V(P)$ as a subset of $[n]$
  \end{itemize}
\item The edge set of the subgraph is
  \begin{itemize}
  \item the edges of $\tau(W)$ corresponding to propagators of $P$
  \item along with the outer edges of $\tau(W)$ for which both their end points are in the vertex set
  \end{itemize}
\end{itemize}
Note that the subgraph $t$ depends on how the propagators of $P$ sit inside $[n]$, not on how they sit in $W_P$ itself.  In particular $t$ is not the subgraph of $\tau(W)$ consisting only of edges corresponding to propagators of $P$.

@@

Our next goal is to show that the dimension of the positroid cell defined by a Wilson loop diagram $(\cP, [n])$ has dimension $3|\cP|$.  Marcott in ***cite this*** has a different proof which is geometric and more elegant, bit it is not easy to track the effect of a particular propagator.  Our approach is much more explicit.

The dimension of a positroid cell is the same as the number of plusses in the associated Le diagram ***cite something***, and so with Algorithm~\ref{alg:put GN on WLD} along with the algorithm for passing from a Grassmann necklace to a Le diagram (reversing Oh's algorithm) described by some of us in \cite{reversingOh}, we can, at the cost of a bit of messy grunt work, give a recursive proof of the $3|\cP|$-dimensionality that explicitly describes the changes in the positions of the plusses in the Le diagram.

@@
